The \dealii{} Library, Version 9.0

### 2018-04-07 9.0/paper.tex
Add myself to the 9.0 paper.

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Denis Davydov,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler
    Matthias Maier
  },
  pdftitle={The deal.II Library, Version 9.0, 2018},
}

@@

 \author[9]{Bruno Turcksin\footnote{
   This manuscript has been authored by UT-Battelle, LLC under Contract No.
   DE-AC05-00OR22725 with the U.S. Department of Energy. The United States
   Government retains and the publisher, by accepting the article for
   publication, acknowledges that the United States Government retains a
   non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce
   the published form of this manuscript, or allow others to do so, for United
   States Government purposes. The Department of Energy will provide public
   access to these results of federally sponsored research in accordance with the
   DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}}
 \affil[9]{Computational Engineering and Energy Sciences Group,
   Computional Sciences and Engineering Division,
   Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
   TN 37831, USA.
   {\texttt{turcksinbr@ornl.gov}}}
%
% \author[10]{David Wells}
% \affil[10]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
% Troy, NY 12180, USA.
%   {\texttt{wellsd2@rpi.edu}}}

@@

% J-P.~Pelteret was supported by the European Research Council (ERC) through the Advanced Grant 289049 MOCOPOLY.
%
B.~Turcksin: This material is based upon work supported by the U.S. Department of
Energy, Office of Science, under contract number DE-AC05-00OR22725.
%
%
% D.~Wells was supported by the National Science Foundation (NSF) through Grant
% DMS-1344962.

>>>>

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Denis Davydov,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler
    Matthias Maier,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.0, 2018},
}

@@

 \author[9]{Bruno Turcksin\footnote{
   This manuscript has been authored by UT-Battelle, LLC under Contract No.
   DE-AC05-00OR22725 with the U.S. Department of Energy. The United States
   Government retains and the publisher, by accepting the article for
   publication, acknowledges that the United States Government retains a
   non-exclusive, paid-up, irrevocable, worldwide license to publish or reproduce
   the published form of this manuscript, or allow others to do so, for United
   States Government purposes. The Department of Energy will provide public
   access to these results of federally sponsored research in accordance with the
   DOE Public Access Plan (http://energy.gov/downloads/doe-public-access-plan).}}
 \affil[9]{Computational Engineering and Energy Sciences Group,
   Computional Sciences and Engineering Division,
   Oak Ridge National Laboratory, 1 Bethel Valley Rd.,
   TN 37831, USA.
   {\texttt{turcksinbr@ornl.gov}}}

\author[10]{David Wells}
\affil[10]{Department of Mathematical Sciences, Rensselaer Polytechnic Institute,
Troy, NY 12180, USA.
  {\texttt{wellsd2@rpi.edu}}}

@@

% J-P.~Pelteret was supported by the European Research Council (ERC) through the Advanced Grant 289049 MOCOPOLY.
%
B.~Turcksin: This material is based upon work supported by the U.S. Department of
Energy, Office of Science, under contract number DE-AC05-00OR22725.

D.~Wells was supported by the National Science Foundation (NSF) through Grant
DMS-1344962.
